### 2019-12-12 manuscript/manuscript.rmd
add Whelan and Ryan phylobayes results

---
bibliography: manuscript.bib
csl: plos.csl
output:
  word_document: default
  html_document: default
  pdf_document: default
  github_document: default
---

>>>>

---
bibliography: manuscript.bib
csl: plos.csl
output:
  html_document: default
  word_document: default
  pdf_document: default
  github_document: default
---
